---
title: "Introducción a Git y GitHub"
author: "Elías, Mirella y Erick"
institute: "Avances en Medición Psicológica"
date: "28/10/2023"
output: 
  xaringan::moon_reader:
    css: [xaringan-themer.css, custom.css]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: 16:11
encoding: "UTF-8"
---

class: inverse, center, middle
# .font150[Qué es git]



```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, warning=FALSE, include=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color       =  "#FF1717",
  padding          = "16px 50px 12px 50px",
  code_font_google = google_font("Fira Mono")
)
```

```{r xaringanExtra, echo=FALSE}
#devtools::install_github("gadenbuie/xaringanExtra")
library(xaringanExtra)
xaringanExtra::use_xaringan_extra(c("tile_view", "tachyons", "panelset"))
xaringanExtra::use_tile_view()
xaringanExtra::use_editable()
xaringanExtra::use_scribble()
xaringanExtra::use_logo(
  image_url ="imagenes/logo.png", 
  link_url = "https://medicionpsicologica.com",
  width = 120, 
  height = 120
  )
xaringanExtra::use_clipboard(
  button_text = "Copiar",
  success_text = "Copiado",
  error_text = "Presiona Ctrl+C para copiar"
)
xaringanExtra::use_fit_screen()
xaringanExtra::use_extra_styles(
  hover_code_line = TRUE,          #<<
  mute_unhighlighted_code = FALSE  #<<
)
```

---
#Git status


Para observar el estado actual de nuestro arbol de trabajo.
git status



---
# Qué es la visualización de datos
.font105[Algunas **definiciones** (Cairo, 2016).]


---

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output


```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

